\documentclass[sigplan]{acmart}

\usepackage[utf8]{inputenc}
\usepackage{url}

\parindent 0cm

\thispagestyle{empty}
\pagestyle{empty}

\begin{document}

\begin{center}
{\bfseries \Huge Chairs' Welcome}
\end{center}

\bigskip
\bigskip
\bigskip
\bigskip

%\large
\noindent
It is our pleasure to welcome you to FARM 2023, the 11th ACM SIGPLAN
International Workshop on Functional Art, Music, Modelling, and
Design! FARM gathers together people from across disciplines who are
harnessing functional techniques in the pursuit of creativity and
expression.

\bigskip

\noindent
Functional Programming has emerged as a mainstream software
development paradigm, and its artistic and creative use is booming. A
growing number of software toolkits, frameworks and environments for
art, music and design now employ functional programming languages and
techniques. FARM is a forum for exploration and critical evaluation of
these developments, for example to consider potential benefits of
greater consistency, tersity, and closer mapping to a problem domain.

\bigskip

\noindent
By gathering researchers, practitioners, artists, designers and anyone
interested, FARM aims to develop this interdisciplinary field. Work in
this challenging area has already led to new language designs,
abstraction techniques, and execution models, as well as the use of
old ideas in new, novel, and surprising ways.

\bigskip

\noindent
The first FARM was held in Boston in 2013, and since then, FARMers
have gathered in Gothenburg, Vancouver, Nara, Oxford, St Louis,
Berlin and Ljubljana, in addition to two online-only meetings in 2020
and 2021. The 2023 edition of FARM will take place in Seattle,
Washington, USA on September 8.

\bigskip

\noindent
FARM 2023 solicited both full papers and demonstrations with
associated extended abstracts. After thorough peer review with
all submissions receiving 3 independent reviews, we accepted 4 full
papers and 2 demonstrations. The final versions of these papers and
demonstration abstracts can all be found in this volume.
As befits our workshop, there is a considerable symmetry among the
submissions with two papers each on the three topics of music,
visualization, and needlework.

\bigskip

\noindent
As in previous editions of FARM there will also be an evening of
performances, this year at the brand new and state of the art Raisbeck Auditorium
at the Cornish College of the Arts, very close to the host
hotel. The evening will begin with a keynote address by world-class concert
pianist Gloria Cheng (UCLA), titled ``Perfectly Imperfect: Music, Math
and the Keyboard'', and continue with a series of diverse performances
combining music, visuals, interaction, and technology. We encourage
you to attend what should be a very memorable evening.

\bigskip

\noindent
Further information about FARM is available on our website,
\url{https://functional-art.org}.

\bigskip

\noindent
We would like to thank ACM and the organizers of ICFP 2023 for their support.
Thanks also to the members of the FARM Program Committee, and to everyone who
submitted papers, demos, and performance proposals.  And, of course, we are
grateful to all of the participants.  We hope that you will enjoy the workshop
as much as we know we will.

\bigskip
\bigskip

\noindent
Welcome to the FARM!

\bigskip
\bigskip
\bigskip
\bigskip

\hskip -.25cm 
\begin{tabular}[t]{l}
 {\bf  Mae Milano}\\
Workshop Chair\\
University of California at Berkeley
\end{tabular}
\hfill
\begin{tabular}[t]{l}
{\bf John Leo}\\
Program Committee Chair\\
Halfaya Research
\end{tabular}
\hfill
\begin{tabular}[t]{l}
{\bf Kaley Eaton}\\
  Performance Chair\\
  Cornish College of the Arts
\end{tabular}
\hfill
\begin{tabular}[t]{l}
  {\bf Michael Sperber}\\
  Publicity Chair\\
  Active Group GmbH
\end{tabular}

\vspace{2mm}


\newpage

\begin{center}
{\bfseries \Huge FARM 2023 Workshop Organization}
\end{center}

\bigskip

\large
\begin{center}
\begin{tabular}{rl}

{\bf Workshop Chair:} & Mae Milano (\emph{University of California at Berkeley})\\
\\

{\bf Program Chair:} & John Leo (\emph{Halfaya Research})\\
\\

{\bf Performance Chair:} & Kaley Eaton (\emph{Cornish College of the Arts})\\
\\

{\bf Publicity Chair:} & Michael Sperber (\emph{Active Group GmbH})\\
\\
  
  {\bf Program Committee:}
  & Youyou	Cong	        (\emph{Tokyo Institute of Technology})\\
  & Visda	Goudarzi        (\emph{Columbia College Chicago})\\
  & John	Hui	        (\emph{Columbia University})\\
  & Oleg	Kiselyov	(\emph{Tohoku University})\\
  & Yoshiki	Ohshima	        (\emph{Croquet Corporation})\\
  & Christopher	Raphael	        (\emph{Indiana University})\\
  & Butch	Rovan	        (\emph{Brown University})\\
  & Chung-chieh	Shan	        (\emph{Indiana University})\\
  & Benjamin	Sherman\\
  & Jeffrey	Snyder	        (\emph{Princeton University})\\
  & Andrew	Sorensen	(\emph{MOSO Corporation})\\
  & Dmitrij	Szamozvancev	(\emph{University of Cambridge})\\
  & Daniel	Winograd-Cort	(\emph{Luminous Computing})\\
  & Halley	Young	        (\emph{University of Pennsylvania})\\
\end{tabular}
\end{center}

\vspace{2mm}

\end{document}

